NMRlipids IV: Headgroup \& glycerol backbone structures, and cation binding in bilayers with PS lipids

### 2018-07-04 Manuscript/manuscriptPS.tex
Update
Update text

@@

    \todo{Berger simulations with NaCl and CaCl to be added} \\

@@

@@

@@

    POPC:POPS (4:1)/Na$^+$  & Lipid14/17 \cite{dickson14,gould18} &0    & 0   & 120:24 & 5760 & ?   & 298  & 300 & 200 & \cite{POPCpopsLIPID17withK}  \\
    POPC:POPS (4:1)/Na$^+$  & Lipid14/17 \cite{dickson14,gould18} &1    & 0   & 102:26 & 4290 & 80  & 310  & 200 & 50 & \cite{POPCpopsBERGERwith1000mMNa}  \\

>>>>

\begin{table*}[!p]

@@

@@

    POPC:POPS (5:1)/K$^+$  & Lipid14/17 \cite{dickson14,gould18} &0  & 0     & 120:24 & 5760 & 0   & 298  & 500 & 200 & \cite{POPCpopsLIPID17withKCI}  \\

@@

    POPC:POPS (5:1)/Na$^+$  & Lipid14/17 \cite{dickson14,gould18} &0   & 0   & 120:24 & 5760 & 0   & 298  & 500 & 200 & \cite{POPCpopsLIPID17withNaCI}  \\
    POPC:POPS (5:1)/Na$^+$  & Lipid14/17 \cite{dickson14,gould18} &0.5  & 0   & 120:24 & 5760 & ?   & 298  & 300 & 200 & \cite{POPCpopsLIPID17withNa}  \\
    POPC:POPS (5:1)/Na$^+$  & Lipid14/17 \cite{dickson14,gould18} &1    & 0   & 120:24 & 5760 & ?   & 298  & 300 & 200 & \cite{POPCpopsLIPID17withNa}  \\
    POPC:POPS (5:1)/Na$^+$  & Lipid14/17 \cite{dickson14,gould18} &2    & 0   & 120:24 & 5760 & ?   & 298  & 300 & 200 & \cite{POPCpopsLIPID17withNa}  \\
    POPC:POPS (5:1)/Na$^+$  & Lipid14/17 \cite{dickson14,gould18} &3    & 0   & 120:24 & 5760 & ?   & 298  & 300 & 200 & \cite{POPCpopsLIPID17withNa}  \\
    POPC:POPS (5:1)/Na$^+$  & Lipid14/17 \cite{dickson14,gould18} &4    & 0   & 120:24 & 5760 & ?   & 298  & 300 & 200 & \cite{POPCpopsLIPID17withNa}  \\
    POPC:POPS (5:1)/Na$^+$ & Lipid14/17 \cite{dickson14,gould18} &0    & 0   & 60:12 & ?     & 0   & 298  & ?  & ?  & \cite{??} \todoi{Data to be delivered by Melcr}  \\
    POPC:POPS (5:1)/Na$^+$ & Lipid14/17 \cite{dickson14,gould18} &0    & 0.03 & 60:12 & ?     & 0   & 298  & ?  & ?  & \cite{??} \todoi{Data to be delivered by Melcr}  \\
    POPC:POPS (5:1)/Na$^+$ & Lipid14/17 \cite{dickson14,gould18} &0    & 0.17 & 60:12 & ?     & 0   & 298  & ?  & ?  & \cite{??} \todoi{Data to be delivered by Melcr}  \\
    POPC:POPS (5:1)/Na$^+$ & Lipid14/17 \cite{dickson14,gould18} &0    & 0.36 & 60:12 & ?     & 0   & 298  & ?  & ?  & \cite{??} \todoi{Data to be delivered by Melcr}  \\

@@

    POPC:POPS (4:1)/Na$^+$  & Berger \cite{tieleman99,mukhopadhyay04} &0    & 0   & 102:26 & 4290 & 0   & 310  & ? & ? & \cite{??} \todoi{To be added by Ollila}  \\
    POPC:POPS (4:1)/Na$^+$  & Berger \cite{tieleman99,mukhopadhyay04}\todoi{Are these correct references?} &1    & 0   & 102:26 & 4290 & 80  & 310  & 200 & 50 & \cite{POPCpopsBERGERwith1000mMNa}  \\
    POPC:POPS (4:1)  & Berger \cite{tieleman99,mukhopadhyay04} &  0  & 0.12   & 104:24 & 4306 & 24 & 310  & 300 & 100 & \cite{POPCpopsBERGERwith102mMCa}  \\
    POPC:POPS (4:1)  & Berger \cite{tieleman99,mukhopadhyay04} &  0  & 0.715  & 104:24 & 4306 & 72 & 310  & 300 & 100 & \cite{POPCpopsBERGERwith715mMCa}  \\
